---
title: "simpleRegress"
author: "Daniel"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a regression simple model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## make a simple regression mode for age

## Model LENGTH ~ AGE  this is an example  

```{r}
AGEmodel <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(AGEmodel)
summary.lm(AGEmodel)
```

## make a simple regression mode for head length
## Model LENGTH ~ HEADLEN  this is an example  

```{r}
HEADLENmodel <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HEADLENmodel)
summary.lm(HEADLENmodel)
```


## make a simple regression mode for head width
## Model LENGTH ~ HEADWTH  this is an example  

```{r}
HEADWTHmodel <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(HEADWTHmodel)
summary.lm(HEADWTHmodel)
```


## make a simple regression mode for CHEST
## Model LENGTH ~ CHEST  this is an example  

```{r}
CHESTmodel <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(CHESTmodel)
summary.lm(CHESTmodel)
```



## make a simple regression mode for WEIGHT
## Model LENGTH ~ WEIGHT  this is an example  

```{r}
WEIGHTmodel <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(WEIGHTmodel)
summary.lm(WEIGHTmodel)
```



# Discussion and Conclusion

Out of all the models and graphs, the best one was Head Length. Seeing as the graph is very close along with others, but the adjusted R-squared for head length is 0.8434 which is the highest and the Residual standard error for it 4.235. The order from best to worst would be HEADLEN at 0.8434, CHEST at 0.7869, NECK at 0.7476, HEADWIT at 0.5321, and then AGE with 0.5073 
